Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
minor

@@

Table~\ref{fig:singlefreq} provides a breakdown of the different type
categories observed at uni-typed positions. Scalar, class and vector are the
most common type categories. The shaded rows correspond to polymorphic
types. Removing those gives us \CountMonomorphicPositions
(\PercMonomorphicPositions) monomorphic positions in a corpus of
\CountPositions parameter and return positions.

>>>>

The next step, is shown in Table~\ref{fig:singlefreq}, the table provides a
breakdown of types occuring in arguments without a union. Scalar, class and
vector are the most common type categories. The shaded rows correspond to
polymorphic types. Removing those gives us \CountMonomorphicPositions
(\PercMonomorphicPositions) monomorphic positions in a corpus of
\CountPositions parameters. With close to 70\% of monomorphic argument or
return values, it is fair to say that even a simple type language provides
significant benefits.

@@
